DynaProg for Scala

### 2012-12-02 docs/roadmap/draft.tex
Nits.
Fixed nasty long-lived bugs, created the reflection version of parsers.
Some more docs.

\subsection*{Abstract}
Dynamic programming is a common pattern of Computer Science used in various domains. Yet underlying matrix recurrences might be difficult to express and error prone. Additionally, domain experts might not have the skills to make an efficient parallel implementation. In this paper, we leverage the Scala / LMS infrastructure to implement a domain specific language (DSL) for dynamic programming on heterogeneous platforms, which allows to write concise and efficient programs. Our contributions are: \ul
\item Classification of DP problems characteristics (matrix shape, dependency graph, ...)
\item State of the art parallel implementation of these classes on GPUs
\item Grammar embedded in Scala (DSL) to express DP problems efficiently
%\item Normalization of the grammar into efficient productions
\item Systematic approach to generate and process backtracking information
\item Code generator to transform a grammar into efficient code for CPU, GPU and FPGA
\ule

@@

% ------------------------------------------------------------------------------------------------
\newpage
\section{Planning --- Work in progress}
\subsubsection*{Steps}\ol
\item Re-implement vanilla combinators with lists
\item Add following problems and features:\ul
	\item Polygon triangulation (cyclic problem) (parallelogram matrix)
	\item SWat with arbitrary gap (multi-track grammar) (rectangular matrix)
	\item Zucker (rules of different complexity $O(n^2) / O(n)$)
	\item Rules normalization
	\item Rules dependency
	\item Automatic backtracking
	\ule
\item Test/proof parsers are correct --- make sure implementation is correct
\item Automate test to compare against implementation
\item Build bottom-up vanilla version\ul
	\item Separate initialization (terminals) and non-terminals (speed up?)
	\item In parallel implement the code generator for CUDA, hardcode in text function bodies for CUDA
	\ule
\item LMS implementation: from normal to Rep/Exp\ul
	\item Re-implement bottom-up vanilla into LMS
	\item Re-implement CUDA version and use functions body to infer CUDA code
	\ule
\item Benchmarks --- compare also versus other papers.
\item Write report
\ole

@@

% ------------------------------------------------------------------------------------------------
\newpage
\bibliographystyle{finplain}
\bibliography{bibliography.bib}
\end{document}

>>>>

\subsection*{Abstract}
Dynamic programming is a common pattern of Computer Science used in various domains. Yet underlying matrix recurrences might be difficult to express and error prone. Additionally, domain experts might not have the skills to make an efficient parallel implementation. In this paper, we leverage the Scala / LMS infrastructure to implement a domain specific language (DSL) for dynamic programming on heterogeneous platforms, which allows to write concise and efficient programs. Our contributions are: \ul
\item {\color{red} Reuse of existing compiler technology for a specific purpose}
%\item Classification of DP problems characteristics (matrix shape, dependency graph, ...)
\item Grammar embedded in Scala (DSL) to express DP problems efficiently
%\item State of the art parallel implementation of these classes on GPUs
%\item Normalization of the grammar into efficient productions
\item Systematic approach to generate and process backtracking information (better than gapc)
\item Code generator to transform a grammar into efficient code for CPU, GPU and FPGA
\ule

@@

% ------------------------------------------------------------------------------------------------
\newpage
\section{Planning --- Work in progress}
\subsection{Write introduction}
\begin{verbatim}
what exists
problem
how we solve it compared to other
how to evaluate
contributions (3): 3 tensed sentences

related work
benchmark => prove by evaluation intro statements
\end{verbatim}

\subsubsection*{Steps}\ol
\item Re-implement vanilla combinators with lists
\item Add following problems and features:\ul
	\item Polygon triangulation (cyclic problem) (parallelogram matrix)
	\item SWat with arbitrary gap (multi-track grammar) (rectangular matrix)
	\item Zucker (rules of different complexity $O(n^2) / O(n)$)
	\item Rules normalization
	\item Rules dependency
	\item Automatic backtracking
	\ule
\item Test/proof parsers are correct --- make sure implementation is correct
\item Automate test to compare against implementation
\item Build bottom-up vanilla version\ul
	\item Separate initialization (terminals) and non-terminals (speed up?)
	\item In parallel implement the code generator for CUDA, hardcode in text function bodies for CUDA
	\ule
\item LMS implementation: from normal to Rep/Exp\ul
	\item Re-implement bottom-up vanilla into LMS
	\item Re-implement CUDA version and use functions body to infer CUDA code
	\ule
\item Benchmarks --- compare also versus other papers.
\item Write report
\ole

@@

% ------------------------------------------------------------------------------------------------
\newpage
\bibliographystyle{plain}
\bibliography{bibliography.bib}
\end{document}
